\cvsection{Education}

\begin{cventries}
	\cventry
	{Master's Degree in Computer Science} % Degree
	{Pontifical Catholic University of Rio Grande do Sul - PUCRS} % Institution
	{Porto Alegre - RS, Brazil} % Location
	{Mar. 2020 - PRESENT} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {I am advised by Ph.D. Dalvan Griebler and a member of GMAP (\href{https://gmap.pucrs.br}{https://gmap.pucrs.br}),\\a group focused on Big Data and in High-Performance Computing (HPC).}
			\item {I am currently working on my dissertation related to the use of machine learning to optimize stream\\processing in multicore architectures.}
			\item {I have a fellowship from SAP.}
		\end{cvitems}
	}

	\cventry
	{Bachelor of Information Systems} % Degree
	{Três de Maio Faculty - SETREM} % Institution
	{Três de Maio - RS, Brazil} % Location
	{Feb. 2015 - Sept. 2019} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Course focused on general understanding of the area of information technology,\\deepening knowledge in software development.}
			\item {The final bachelor's thesis was related to the use of deep learning in agriculture.}
		\end{cvitems}
	}

	\cventry
	{Technical Course in Computer Science} % Degree
	{Três de Maio Faculty - SETREM} % Institution
	{Três de Maio - RS, Brazil} % Location
	{Jan. 2013 - Jan. 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Course with main focus on system design, analysis and development.}
		\end{cvitems}
	}
\end{cventries}
